---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(economicIndicators)
```


## Background

This package provides an analysis of crucial indicators such as population, the AMA exchange rate, and GDP per population of a country within the years 1970-2021 with the economicIndiators_data dataset from Kaggle. You must use the specific data frame given in the package to make these functions work. Other data frames will not be able to use the functions because of how to functions were created.

What you can do with the package:

-   Find the Highest GDP in a given Year

-   Find the Lowest GDP in a given Year

-   Find the Mean GDP in a given Year

-   Learn a country's AMA Exchange Rate

-   Learn the Agriculture and nature indicator of a country

-   Compare the Population of 2 countries

-   Discover the GDP per population in a specific year.

-   Visualize and find out the line for the country's GDP per population over time.

## Highest GDP Per Year

It provides the highest gdp value based on the given year.

Example:

```{r}
highest_gdp_per_year(economicIndicators_data, 1970)
```

The example shows that the United States had the highest Gross Domestic Product (GDP) in 1970 of about 1.07e+12.

## Lowest GDP Per Year

It provides the lowest gdp value based on the given year.

Example:

```{r}
lowest_gdp_per_year(economicIndicators_data, 1970)
```

The example shows that Tuvalu had the lowest Gross Domestic Product (GDP) in 1970 of about 2585174.

## Mean GDP Per Year

It provides the mean gdp value based on the given year.

Example:

```{r}
mean_gdp_per_year(economicIndicators_data, 1970)
```

The example shows that the mean Gross Domestic Product (GDP) in 1970 of about 18243661311.


## AMA Exchange Rate

The AMA exchange rate function provides the AMA exchange rate of a country in a certain year.

Example:

```{r}
ama_exchange_rate(economicIndicators_data,'Spain', 1970)
```

This shows that tehe MA Exchange Rate of Spain in 1970 has a value of 0.4207085.

## Country GDP Per Population over Time

It provides what was a country's GDP per population over the span of 1970-2021.

```{r}
country_GDP_per_pop_timed(economicIndicators_data,'Spain')
```

This function provides the regression model of Spain's GDP per population from 1970-2021 and a time series graph of Spain's GDP per population over time.

## GDP per population in a specific year

The function provides what was the GDP per population of a country set in a specific year.

```{r}
gdp_per_pop1yr(economicIndicators_data,'Spain', 1970)
```

This provides the GDP per population of Spain in 1970.

## Population Comparison in a year

The function provides the comparison of two different countries set in a specific year.

Example:

```{r}
pop_country_compare_1year(economicIndicators_data,'Spain', 'Italy', 1970)
```

The example states what was the population of Spain and Italy were in 1970.

## Agriculture and nature

The function provides the indicator of agriculture, hunting, forestry, fishing production.

Example:

```{r}
ag_hunt_nature(economicIndicators_data,'Spain', 1970)

```

The example here shows that the production of nature, agriculture,and hunting of Spain in 1970 was 3904684420.


## Common Uses

```{r}
# Outputs a list of every higheset gdp per year for every year 
list <- lapply(unique(economicIndicators_data$Year), function(x) {
    highest_gdp_per_year(economicIndicators_data, x)
})
```

